Describe and Explore: Using feature-based time-series clustering to understand modern intensive longitudinal data (Working Title)

### 2022-11-27 manuscript.tex
:construction: illust intro pos
:construction: expl intro

\section{Empirical Implementation/Illustration}
% Methods and Results from RMarkdown render
\input{methods-and-results}

@@

\citep[][]{Madley-Dowd2019} [proportion of missing data and imputations]

>>>>

\section{Empirical Implementation/Illustration}
To illustrate the use case of the feature-based time series with psychological ESM data, we ....

Something about the migration experience literature should go here as part of the illustration intro ...

% Methods and Results from RMarkdown render
\input{methods-and-results}

@@
